Model Samples Processing

### 2020-02-12 stats/model_sample_processing.Rmd
test run mixture model

@@

>>>>

# combine chains into one file

@@

# mixture model

model <- bind_rows(
 fread("../webppl/output/samples-fullBayes-mixtureModel-reFactor-noRandomEffects_mcmc-1000_burn500_lag5_chain1.csv",header = T)%>%mutate(chain = 1)
)

saveRDS(item_params, "../saves/item_params_mm.rds")

saveRDS(global_params, "../saves/global_params_mm.rds")

saveRDS(item_sigma, "../saves/item_sigma_mm.rds")

mixture<- model %>%
  filter(b == "mixtureComponent")%>%
  select(b,g,chain)%>%
    rename(parameter = b,
         p_informative = g)

saveRDS(mixture, "../saves/mixture_mm.rds")

model_pred_prag <- model %>%
  filter(a == "modelPrediction",
         b == "mixtureModel")%>%
  select(-a, -h, -c)%>%
  rename(model = b, 
         alignment = d,
         item = e,
         age = f, 
         pred = g)

saveRDS(model_pred_prag, "../saves/model_pred_mm.rds")
